\begin{thebibliography}{10}

\bibitem{10.1257/jep.31.2.211}
Hunt Allcott and Matthew Gentzkow.
 Social media and fake news in the 2016 election.
 {\em Journal of Economic Perspectives}, 31(2):211--36, 5 2017.

\bibitem{Granik8100379}
M.~Granik and V.~Mesyura.
 Fake news detection using naive bayes classifier.
 In {\em 2017 IEEE First Ukraine Conference on Electrical and Computer
  Engineering (UKRCON)}, pages 900--903, 5 2017.

\bibitem{Gilda8305411}
S.~Gilda.
 Evaluating machine learning algorithms for fake news detection.
 In {\em 2017 IEEE 15th Student Conference on Research and Development
  (SCOReD)}, pages 110--115, 12 2017.

\bibitem{松尾省吾2018master}
松尾 省吾.
 機械学習を用いた流言の検出に関する研究.
 Master's thesis, 電気通信大学院, 2018.

\bibitem{Wu:2018:TFF:3159652.3159677}
Liang Wu and Huan Liu.
 Tracing fake-news footprints: Characterizing social media messages by
  how they propagate.
 In {\em Proceedings of the Eleventh ACM International Conference on
  Web Search and Data Mining}, WSDM '18, pages 637--645, New York, NY, USA,
  2018. ACM.

\bibitem{W16-0802}
Victoria Rubin, Niall Conroy, Yimin Chen, and Sarah Cornwell.
 Fake news or truth? using satirical cues to detect potentially
  misleading news.
 In {\em Proceedings of the Second Workshop on Computational
  Approaches to Deception Detection}, pages 7--17. Association for
  Computational Linguistics, 2016.

\bibitem{DBLP:journals/corr/HorneA17}
Benjamin~D. Horne and Sibel Adali.
 This just in: Fake news packs a lot in title, uses simpler,
  repetitive content in text body, more similar to satire than real news.
 {\em CoRR}, abs/1703.09398, 2017.

\bibitem{Jin:2017:MFR:3123266.3123454}
Zhiwei Jin, Juan Cao, Han Guo, Yongdong Zhang, and Jiebo Luo.
 Multimodal fusion with recurrent neural networks for rumor detection
  on microblogs.
 In {\em Proceedings of the 25th ACM International Conference on
  Multimedia}, MM '17, pages 795--816, New York, NY, USA, 2017. ACM.

\bibitem{Wang:2018:EEA:3219819.3219903}
Yaqing Wang, Fenglong Ma, Zhiwei Jin, Ye~Yuan, Guangxu Xun, Kishlay Jha, Lu~Su,
  and Jing Gao.
 Eann: Event adversarial neural networks for multi-modal fake news
  detection.
 In {\em Proceedings of the 24th ACM SIGKDD International Conference
  on Knowledge Discovery \&\#38; Data Mining}, KDD '18, pages 849--857, New
  York, NY, USA, 2018. ACM.

\bibitem{DBLP:journals/corr/SimonyanZ14a}
Karen Simonyan and Andrew Zisserman.
 Very deep convolutional networks for large-scale image recognition.
 {\em CoRR}, abs/1409.1556, 2014.

\bibitem{DBLP:journals/corr/Kim14f}
Yoon Kim.
 Convolutional neural networks for sentence classification.
 {\em CoRR}, abs/1408.5882, 2014.

\bibitem{7298935}
O.~Vinyals, A.~Toshev, S.~Bengio, and D.~Erhan.
 Show and tell: A neural image caption generator.
 In {\em 2015 IEEE Conference on Computer Vision and Pattern
  Recognition (CVPR)}, pages 3156--3164, 6 2015.

\bibitem{7410636}
S.~Antol, A.~Agrawal, J.~Lu, M.~Mitchell, D.~Batra, C.~L. Zitnick, and
  D.~Parikh.
 Vqa: Visual question answering.
 In {\em 2015 IEEE International Conference on Computer Vision
  (ICCV)}, pages 2425--2433, 12 2015.

\bibitem{holan_2018}
Angie~Drobnic Holan.
 The principles of the truth-o-meter: How we fact-check, 2 2018.

\bibitem{tamir}
Mike Tamir.
 About fakerfact.

\bibitem{harmanci_2012}
Reyhan Harmanci.
 11 viral photos that aren't hurricane sandy, 10 2012.

\bibitem{collobert2011natural}
Ronan Collobert, Jason Weston, L{\'e}on Bottou, Michael Karlen, Koray
  Kavukcuoglu, and Pavel Kuksa.
 Natural language processing (almost) from scratch.
 {\em Journal of Machine Learning Research}, 12(Aug):2493--2537, 2011.

\bibitem{KalchbrennerACL2014}
Nal Kalchbrenner, Edward Grefenstette, and Phil Blunsom.
 A convolutional neural network for modelling sentences.
 {\em Proceedings of the 52nd Annual Meeting of the Association for
  Computational Linguistics}, 6 2014.

\bibitem{JMLR:v15:srivastava14a}
Nitish Srivastava, Geoffrey Hinton, Alex Krizhevsky, Ilya Sutskever, and Ruslan
  Salakhutdinov.
 Dropout: A simple way to prevent neural networks from overfitting.
 {\em Journal of Machine Learning Research}, 15:1929--1958, 2014.

\bibitem{DBLP:journals/corr/KingmaB14}
Diederik~P. Kingma and Jimmy Ba.
 Adam: {A} method for stochastic optimization.
 {\em CoRR}, abs/1412.6980, 2014.

\bibitem{boididou2015verifying}
Christina Boididou, Katerina Andreadou, Symeon Papadopoulos, Duc-Tien
  Dang-Nguyen, Giulia Boato, Michael Riegler, Yiannis Kompatsiaris, et~al.
 Verifying multimedia use at mediaeval 2015.
 In {\em MediaEval}, 2015.

\bibitem{google_2013}
Tomas Mikolov and Ilya Sutskever.
 Google code archive - long-term storage for google code project
  hosting., 7 2013.

\bibitem{Vosoughi:2016:TLT:2911451.2914762}
Soroush Vosoughi, Prashanth Vijayaraghavan, and Deb Roy.
 Tweet2vec: Learning tweet embeddings using character-level cnn-lstm
  encoder-decoder.
 In {\em Proceedings of the 39th International ACM SIGIR Conference on
  Research and Development in Information Retrieval}, SIGIR '16, pages
  1041--1044, New York, NY, USA, 2016. ACM.

\end{thebibliography}
